### 2024-06-15 research-methods.qmd
20240615 - typos

### Conclusion Validity {#sec-externalValidity}

@@

When one mechanism fully accounts for the effect of the predictor variable on the outcome variable, this is known as **full mediation**, as depicted in @fullMediation:

@@

When a single process partially—but does not fully—accounts for the effect of the predictor variable on the outcome variable; this is known as **partial mediation** and is depicted in @fig-fullMediation:

::: {#fig-fullMediation}
![](images/mediationPartial.png)

@@

For example, if the effect of consuming sports drinks on player performance differs for Quarterbacks and Wide Receivers, the interaction could be depicted in @moderationExamplePathDiagram and @fig-moderationExampleInteractionGraph:

>>>>

### Conclusion Validity {#sec-conclusionValidity}

@@

When one mechanism fully accounts for the effect of the predictor variable on the outcome variable, this is known as **full mediation**, as depicted in @fig-fullMediation:

@@

When a single process partially—but does not fully—accounts for the effect of the predictor variable on the outcome variable; this is known as **partial mediation** and is depicted in @fig-partialMediation:

::: {#fig-partialMediation}
![](images/mediationPartial.png)

@@

For example, if the effect of consuming sports drinks on player performance differs for Quarterbacks and Wide Receivers, the interaction could be depicted in @fig-moderationExamplePathDiagram and @fig-moderationExampleInteractionGraph:
